2016 Brussels Bombings

### 2019-07-13 report/paper.Rmd
Remove option to render html in pdf

---
title: '2016 Brussels Bombings'
subtitle: 'Air Traffic Analysis'
author:
- Ramiro Balado Ordax
- Alejandro Hernández Rubio
- Pol Mesalles Ripoll
output:
    pdf_document:
        highlight: tango
        number_sections: true
        keep_tex: true
header-includes:
- \usepackage{subfig}
always_allow_html: true
---

>>>>

---
title: '2016 Brussels Bombings'
subtitle: 'Air Traffic Analysis'
author:
- Ramiro Balado Ordax
- Alejandro Hernández Rubio
- Pol Mesalles Ripoll
output:
    pdf_document:
        highlight: tango
        number_sections: true
        keep_tex: true
header-includes:
- \usepackage{subfig}
---
